Methods for Large Scale Learning to Rank

### 2014-04-03 report/Chapters/CrossBenchmarkComparison.tex
Structuur Cross Benchmark comparison verbeterd

As we have seen in chapter~\ref{chap:benchmark_results}, evaluation of Learning-to-Rank methods is spread out over the several benchmark datasets. However, as the evaluated Learning-to-Rank methods differ from benchmark to benchmark, no single benchmark comparison can be regarded as a conclusive argument on which Learning-to-Rank method is most accurate. Several studies make a small start in considering Learning-to-Rank method performance over multiple benchmark datasets. Gomes et al. \cite{Gomes2013} analysed ranking accuracy of a set of models over both LETOR 3.0 and LETOR 4.0. Busa-Fekete et al. \cite{Busa-Fekete2013} compared the accuracy of a small set of models over the LETOR 4.0 datasets, both MSLR datasets, both Yahoo! Learning to Rank Challenge datasets and the OHSUMED dataset from LETOR 3.0. To my knowledge, no large-scale accuracy meta-analysis has been conducted where published evaluation results on several benchmark datasets are taken into account.\\

\subsection{Comparison methodology}
With a meta-analysis I will compare the performance of Learning-to-Rank methods across the Learning-to-Rank benchmark datasets described in foregoing sections. With a literature review I will collect evaluation results on the datasets/collections. The following list presents an overview of the benchmark collections taken into account in the meta-analysis:
\begin{itemize}
\item LETOR 2.0
\item LETOR 3.0
\item LETOR 4.0
\item Yahoo! Learning to Rank Challenge
\item Yandex Internet Mathematics Competition 2009
\item MSLR-web10/30k
\item WCL2R
\item AOL
\end{itemize}

@@

\begin{table}
\begin{tabular}{l|l}
Benchmark & Google scholar search results \\
\hline
LETOR 4.0 & 75 results \\
MSLR-web10k & 16 results \\
MSLR-web30k & 15 results \\
Yandex Internet Mathematics Competition & 1 result \\ 
\end{tabular}
\caption{Google scholar search results for Learning-to-Rank benchmarks}
\label{tbl:ltr_benchmark_searchres}
\end{table}

The LETOR 3.0 paper \cite{Qin2010} states that it may differ between datasets what the most accurate ranking methods are. To evaluate the overall performance of Learning-to-Rank methods over the multiple datasets in the LETOR 3.0 collections, Qin et al. \cite{Qin2010} proposed a measure called \emph{winning number} as the number of other algorithms that an algorithm can beat over the set of datasets. Formally the winning number measure is defined as\\

@@

%TODO: waarom ndcg@3,5,10 en MAP?$
%TODO: limitations van deze vergelijkingsmethodologie$

>>>>

As we have seen in chapter~\ref{chap:benchmark_results}, evaluation of Learning-to-Rank methods is spread out over the several benchmark datasets. However, as the evaluated Learning-to-Rank methods differ from benchmark to benchmark, no single benchmark comparison can be regarded as a conclusive argument on which Learning-to-Rank method is most accurate.\\

Several studies make a small start in considering Learning-to-Rank method performance over multiple benchmark datasets. Gomes et al. \cite{Gomes2013} analysed ranking accuracy of a set of models over both LETOR 3.0 and LETOR 4.0. Busa-Fekete et al. \cite{Busa-Fekete2013} compared the accuracy of a small set of models over the LETOR 4.0 datasets, both MSLR datasets, both Yahoo! Learning to Rank Challenge datasets and the OHSUMED dataset from LETOR 3.0. To my knowledge, no large-scale accuracy meta-analysis has been conducted where published evaluation results on several benchmark datasets are taken into account. With a meta-analysis I will compare the performance of Learning-to-Rank methods across the Learning-to-Rank benchmark datasets described in foregoing sections.

\section{Collecting evaluation measurements}
With a literature review I will collect evaluation results on the datasets/collections. The following list presents an overview of the benchmark collections taken into account in the meta-analysis:
\begin{itemize}
\item LETOR 2.0
\item LETOR 3.0
\item LETOR 4.0
\item Yahoo! Learning to Rank Challenge
\item Yandex Internet Mathematics Competition 2009
\item MSLR-web10/30k
\item WCL2R
\item AOL
\end{itemize}

@@

\begin{table}[!h]
\begin{tabular}{l|l}
Benchmark & Google scholar search results \\
\hline
LETOR 4.0 & 75 results \\
MSLR-web10k & 16 results \\
MSLR-web30k & 15 results \\
Yandex Internet Mathematics Competition & 1 result \\ 
\end{tabular}
\caption{Google scholar search results for Learning-to-Rank benchmarks}
\label{tbl:ltr_benchmark_searchres}
\end{table}

\section{Comparison methodology}
The LETOR 3.0 paper \cite{Qin2010} states that it may differ between datasets what the most accurate ranking methods are. To evaluate the overall performance of Learning-to-Rank methods over the multiple datasets in the LETOR 3.0 collections, Qin et al. \cite{Qin2010} proposed a measure called \emph{winning number} as the number of other algorithms that an algorithm can beat over the set of datasets. Formally the winning number measure is defined as\\

@@

\section{Results \& Discussion}
\begin{figure}[!h]
\includegraphics[scale=0.40]{gfx/combined_normalized_winnum}
\caption{Cross-benchmark comparison of Learning-to-Rank methods}
\label{fig:normalised_winning_number_all}
\end{figure}
%TODO: waarom ndcg@3,5,10 en MAP?$
%TODO: limitations van deze vergelijkingsmethodologie$

\section{Limitations}
